Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change

### 2025-10-13 paper/paper.qmd
Remove unnecessary parentheses
Fix grammar

![Number of years reef coral cover exceeds the assumed carbonate budget threshold in terms
of coral cover ($\theta_0$) between 2025 to 2075 (y-axis) under ACCESS-ESM1-5. Left panel
shows the relationship between reef median depth, while the right panel shows the same for
log10-weighted incoming connectivity. Point colour (purple to yellow) represents
($\theta_0$), with brighter shades indicating a higher $\theta_0$. Deeper reefs have an
increased number of years above the considered range of $\theta_0$, while no relationship
between weighted incoming connectivity and carbonate budget maintenance was
found.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
fig-align="center" width="14.82cm"}

@@

It is a common conclusion in coral reef ecology that a primary facet of reef resilience is
the supply of recruits that a reef receives following disturbance [@hock2017; @mumby2008;
@torres2024]. No direct, first order, relationship between weighted incoming connectivity
and the ability of reefs to maintain positive carbonate budgets under future conditions was
found. There has been contrasting evidence [@bode2018; @hock2017] surrounding whether recent
generation connectivity modelling is able to identify reefs that are important for recovery
processes, with findings dependent on the larval connectivity model used. These
investigations were performed using prior generations of larval connectivity models
parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods, without
considering the influence of reef depth on resilience. Using updated 1km^2^ resolution
larval connectivity across the whole GBR, with a limited temporal sample of particle flows,
it was found that larval connectivity alone may not be important or reef resilience and
recovery but should be considered in combination with more influential factors such as
depth.

>>>>

![Number of years reef coral cover exceeds the assumed carbonate budget threshold in terms
of coral cover ($\theta_0$) between 2025 to 2075 (y-axis) under ACCESS-ESM1-5. Left panel
shows the relationship between reef median depth, while the right panel shows the same for
log10-weighted incoming connectivity. Marker colour (purple to yellow) represents
$\theta_0$, with brighter shades indicating a higher $\theta_0$. Deeper reefs have an
increased number of years above the considered range of $\theta_0$, while no relationship
between weighted incoming connectivity and carbonate budget maintenance was
found.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
fig-align="center" width="14.82cm"}

@@

It is a common conclusion in coral reef ecology that a primary facet of reef resilience is
the supply of recruits that a reef receives following disturbance [@hock2017; @mumby2008;
@torres2024]. No direct, first order, relationship between weighted incoming connectivity
and the ability of reefs to maintain positive carbonate budgets under future conditions was
found. There has been contrasting evidence [@bode2018; @hock2017] as to whether current
connectivity modelling is able to identify reefs that are important for recovery
processes, with findings dependent on the larval connectivity model used. These
investigations were performed using prior generations of larval connectivity models
parameterised for 2008-2013 [@hock2017] and 1996-2002 [@bode2018] time periods, without
considering the influence of reef depth on resilience. Using updated 1km^2^ resolution
larval connectivity across the whole GBR, with a limited temporal sample of particle flows,
it was found that larval connectivity alone may not be important or reef resilience and
recovery but should be considered in combination with more influential factors such as
depth.
